---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BCSreg

<!-- badges: start -->
[![R-CMD-check](https://github.com/ffqueiroz/BCSreg/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ffqueiroz/BCSreg/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The `BCSreg` package provides tools for fitting Box-Cox symmetric (BCS) and zero-adjusted BCS regression models. It includes diagnostic tools for the fitted models, such as residual analysis, local influence measures, and goodness-of-fit statistics.

## Installation

You can install the development version of `BCSreg` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ffqueiroz/BCSreg")
```

## Main functions

#### Implementation of the Box-Cox symmetric class of distributions

The package currently supports eight members of the BCS class of distributions: 

- Box-Cox hyperbolic,
- Box-Cox type I logistic, 
- Box-Cox type II logistic, 
- Box-Cox normal, 
- Box-Cox power exponential, 
- Box-Cox sinh-normal, 
- Box-Cox slash, 
- Box-Cox $t$. 

The following functions are provided to work with these distributions:

```{r usage functions BCS, eval=FALSE}
dBCS(x, mu, sigma, lambda, zeta, family = "NO", log = FALSE)

pBCS(q, mu, sigma, lambda, zeta, family = "NO", lower.tail = TRUE, log.p = FALSE)

qBCS(p, mu, sigma, lambda, zeta, family = "NO", lower.tail = TRUE, log.p = FALSE)

rBCS(n, mu, sigma, lambda, zeta, family = "NO")
```


#### Implementation of the zero-adjusted Box-Cox symmetric class of distributions

The package also implements zero-adjusted versions of the BCS distributions, suitable for modeling non-negative data with an excess of zeros. The supported families are the zero-adjusted versions of the same eight BCS distributions listed above.

Corresponding functions include:

```{r usage functions ZABCS, eval=FALSE}
dZABCS(x, alpha, mu, sigma, lambda, zeta, family = "NO", log = FALSE)

pZABCS(q, alpha, mu, sigma, lambda, zeta, family = "NO", lower.tail = TRUE, log.p = FALSE)

qZABCS(p, alpha, mu, sigma, lambda, zeta, family = "NO", lower.tail = TRUE, log.p = FALSE)

rZABCS(n, alpha, mu, sigma, lambda, zeta, family = "NO")
```

#### `BCSreg` 

The main function of the package is `BCSreg()`, which fits either a BCS or a zero-adjusted BCS regression model to non-negative data. Its usage is:

```{r PLregfunction, eval = FALSE}
BCSreg(formula, data, subset, na.action, family = "NO", zeta, link = "log", sigma.link = "log", 
       alpha.link, control = BCSreg.control(...), model = FALSE, y = FALSE, x = FALSE, ...)
```

The function returns an object of class `"BCSreg"`, which supports generic methods such as `print()`, `summary()`, `plot()`, `residuals()`, among others.

#### `extra.parameter` 

An important utility in the package is the `extra.parameter()` function, which estimates the extra parameter for certain BCS and zero-adjusted models. Its usage is:

```{r extraparameter, eval = FALSE}
extra.parameter(object, family, grid = seq(1, 30, 2), trace = TRUE, plot = TRUE,
                control = BCSreg.control(...), ...)
```

## Reference

Medeiros, R. M. R., and Queiroz, F. F. (2025). *Flexible modeling of non-negative continuous data: Box-Cox symmetric regression and its zero-adjusted extension*.
